How do we copy and paste? The semantic drift of quotations in blogspace

### 2015-03-05 brains-introduction.tex

Broadly speaking, we may distinguish two main research streams, depending on whether the focus lies on cognitive processes or on social dynamics. A first stream is largely structured around cultural anthropology and essentially addresses cultural similarity, diversity and its evolution. It features several theories mixing social and individual cognition including, to cite a few, the debated ``memetic'' program initiated by \citet{Dawkins76} (for which the collection of works by \citet{Aunger00} provides a solid overview), the development of evolutionary models of norms (see for instance \citet{Ehrlich05}) following the seminal work of \citet{Boyd85}); or the ``cultural epidemiology'' program proposed by \citet{sper:expl}, which links the concept of mental representation to the concept of public representation (the latter being the counterpart of the former outside of the brain, \hbox{i.e.} in all sorts of cultural artifacts: texts, utterances, etc.).
%\footnote{\citet{sper:expl} emphasizes this distinction in his seminal work: ``A representation may exist inside its user: it is then a \emph{mental representation}, such as a memory, a belief, or an intention. The producer and the user of a mental representation are one and the same person. A representation may also exist in the environment of its user, as is the case, for instance, of the text you are presently reading: it is then a \emph{public representation}''.}

One of the core claims of this literature consists in emphasizing that not all knowledge is equally fit for being reproduced, although the various approaches have a different take on how exactly this notion of fitness should be operationalized. Sperber's cultural epidemiology classically opposes Dawkins' memetics by insisting that representations are not being replicated through a high-fidelity copy process, but are being interpreted and produced anew, and are thus greatly subject to change.
Cultural epidemiology postulates that this conceptual evolution can be appraised through the notion of ``cultural attractor'', seen as the attraction domain of an underlying socio-semantic dynamical system.\footnote{Works such as \citet{Atran03} argue that this approach is anthropologically better suited than memetics, and some of the main issues in this debate are further detailed by \citet{Kuper00} and \citet{Bloch00}.}
Despite some recent modeling attempts (\hbox{e.g.} \citet{Claidiere07}), the development of quantitative measurements relying on the concept of cultural attractors has remained a relatively hard task and, to our knowledge, this hypothesis has not yet been empirically analyzed in an extensive manner.

Another research stream deals with rather macroscopic studies of knowledge diffusion. Here, one of the focal points is that not all knowledge gets propagated identically along the same routes, within the same communities, at the same pace. The various approaches usually feature a minimalistic description of cognitive processes, strongly reminiscent of biological epidemiology (a single, atomic piece of information may or may not be adopted by each individual).  
This research program nonetheless exhibits a particularly interesting empirical track record --- largely owing to a recent avalanche of observable \emph{in vivo} data which, for a good decade now, have mainly come from online interaction contexts.
While these information trails are not records of ``physical'' inter-individual interactions (in the sense of ``real life'' interactions), they still constitute a wealth of observations on the dynamics of public --~albeit online~-- representations.
Some authors could describe for instance the propagation of cultural artifacts across social networks such as blogspace \citep{Gruhl04}, the characteristic times and diffusion cycles both within these social networks and with respect to the topical dynamics of news media \citep{Leskovec09}, or the reciprocal influence between the social network topology and the distribution of issues \citep{Cointet09}.

@@

The practical study of the transformation of public representations has emerged only recently.
For one, models involving evolution and representations to study the notion of ``cultural attractor'' have appeared only a few years ago (see \citet{Claidiere07,claidiere2014darwinian} as well as a hybrid empirical-theoretical protocol in \citet{maccallum2012evolution}).
Among the empirical approaches, some of the most relevant studies to date consist in a series of papers investigating \emph{quotation} transformations in a large corpus of US blog posts, initially collected and studied by \citet{Leskovec09} and further analyzed by \citet{Simmons11} and \citet{omod-mult}.
%They exhibit several types of regularities and propose diffusion-transformation models of the evolution of quotations, which may nonetheless appear to be relatively simplistic from a cognitive viewpoint. One of the main observations in these works is that even for quotations, a type of public representation that should be among the most stable, it is still possible to witness significant transformations. However, these studies address transformations by focusing on the properties of the source of the quotation (\hbox{e.g.} news outlet {vs.} blog), or the surrounding public space (\hbox{e.g.} quotation frequency in the corpus), rather than the very cognitive-level features which may determine or, at least, influence these transformations.
One of the main observations in these works is that even for quotations, a type of public representation that should be among the most stable, it is still possible to witness significant transformations. They essentially examine the effect of some properties of the quotation source (\hbox{e.g.} news outlet {vs.} blog) or of the surrounding public space (\hbox{e.g.} quotation frequency in the corpus). Some diffusion-transformation models have been proposed, yet the very cognitive features which may determine or, at least, influence these transformations, are overlooked; which may appear to be relatively unsatisfying from a cognitive viewpoint.

At this level, we have to turn to the broader psycholinguistic literature which provides one of the main cognitive foundations for public representation evolution by studying the influence of word features on the ease of recall.
This field is well developed and details the impact that classical psycholinguistic variables such as word frequency (see \citet{Yonelinas02} for a review), age-of-acquisition \citep{Zevin02}, number of phonemes or number of syllables (see for instance \citet{Rey98} and \citet{nick-diss}), have in this type of task.

Less classical linguistic variables, based on the study of semantic network properties, have recently started to be used, in the context of connectionism and its normative processual models (see for instance \citet{collins1975spreading}).
Let us mention four interesting studies on that matter, which demonstrate in a strictly \emph{in vitro} framework and at the vocabulary level that properties computed on a word network are important factors for the cognitive processes and reproduction of those words.
First, \citet{Griffiths07} analyze a task where subjects are asked to name the first word which comes to their mind when they are presented with a random letter from the %Latin
alphabet. The authors show that there exists a link between the ease of recall of words and one of their semantic features, namely their authority position (pagerank) in a language-wide semantic network built from external word association data.
\citet{austerweil2012human} further develop this idea by showing that random walk on such a semantic network, that is the exact process measured by the pagerank index, gives a parsimonious account of some semantic retrieval effects (namely, related items being retrieved together).
A third psycholinguistic study by \citet{Chan10} shows, in a picture-naming task, that words are produced faster and with fewer mistakes when they have a lower clustering coefficient in an underlying phonological network (which, again, is  defined from external phonological data).
\citet{nelson2013activation}, finally, show the importance of clustering coefficient in a semantic network by studying the role it plays in a variety of recall and recognition tasks (extralist and intralist cuing, single item recognition, and primed free assocation).

On the whole, the current psycholinguistic state-of-the-art seems to hint towards two antagonistic types of results.
On one hand, part of the literature tends to show that recall is easier for the least ``awkward'' words; those whose age of acquisition is earlier, length is smaller, semantic network position is more central -- this is particularly true in tasks where participants are asked to form spontaneous associations or utter a word in response to a given signal.
On the other hand, when the task consists in recognizing a specific item in a list, ``awkward'' words are actually more easily remembered, possibly as they are more informative and plausibly more discernible (see again~\citet{Yonelinas02} for a review).
The jury is still out as to whether reformulation alteration, that is spontaneous replacement of words when asked to repeat a given utterance, is rather of the former or latter sort.
We also aim here at shedding some light on this debate, considering oddness as a dimension of the purported fitness of utterances.

>>>>

Broadly speaking, we may distinguish two main research streams, depending on whether the focus lies on cognitive processes or on social dynamics. A first stream is largely structured around cultural anthropology and essentially addresses cultural similarity, diversity and its evolution. It features several theories mixing social and individual cognition including, to cite a few, the debated ``memetic'' program initiated by \citet{Dawkins76} (for which the collection of works by \citealp{Aunger00}, provides a solid overview), the development of evolutionary models of norms~\citep[see for instance][]{Ehrlich05} following the seminal work of \citet{Boyd85}; or the ``cultural epidemiology'' program proposed by \citet{sper:expl}, which links the concept of mental representation to the concept of public representation (the latter being the counterpart of the former outside of the brain, \hbox{i.e.} in all sorts of cultural artifacts: texts, utterances, etc.).
%\footnote{\citet{sper:expl} emphasizes this distinction in his seminal work: ``A representation may exist inside its user: it is then a \emph{mental representation}, such as a memory, a belief, or an intention. The producer and the user of a mental representation are one and the same person. A representation may also exist in the environment of its user, as is the case, for instance, of the text you are presently reading: it is then a \emph{public representation}''.}

One of the core claims of this literature consists in emphasizing that not all knowledge is equally fit for being reproduced, although the various approaches have a different take on how exactly this notion of fitness should be operationalized. Sperber's cultural epidemiology classically opposes Dawkins' memetics by insisting that representations are not being replicated through a high-fidelity copy process, but are being interpreted and produced anew, and are thus greatly subject to change.
Cultural epidemiology postulates that this conceptual evolution can be appraised through the notion of ``cultural attractor'', seen as the attraction domain of an underlying socio-semantic dynamical system.\footnote{Works such as \citet{Atran03} argue that this approach is anthropologically better suited than memetics, and some of the main issues in this debate are further detailed by \citet{Kuper00} and \citet{Bloch00}.}
Despite some recent modeling attempts~\citep[e.g.][]{Claidiere07}, the development of quantitative measurements relying on the concept of cultural attractors has remained a relatively hard task and, to our knowledge, this hypothesis has not yet been empirically analyzed in an extensive manner.

Another research stream deals with rather macroscopic studies of knowledge diffusion. Here, one of the focal points is that not all knowledge gets propagated identically along the same routes, within the same communities, at the same pace. The various approaches usually feature a minimalistic description of cognitive processes, strongly reminiscent of biological epidemiology (a single, atomic piece of information may or may not be adopted by each individual).  
This research program nonetheless exhibits a particularly interesting empirical track record --- largely owing to a recent avalanche of observable \emph{in vivo} data which, for a good decade now, have mainly come from online interaction contexts.
While these information trails are not records of ``physical'' inter-individual interactions (in the sense of ``real life'' interactions), they still constitute a wealth of observations on the dynamics of public --~albeit online~-- representations.
Some authors could describe for instance the propagation of cultural artifacts across social networks such as blogspace~\citep{Gruhl04}, the characteristic times and diffusion cycles both within these social networks and with respect to the topical dynamics of news media~\citep{Leskovec09}, or the reciprocal influence between the social network topology and the distribution of issues~\citep{Cointet09}.

@@

The practical study of the transformation of public representations has emerged only recently.
For one, models involving evolution and representations to study the notion of ``cultural attractor'' have appeared only a few years ago (see \citealp{Claidiere07}, and \citealp{claidiere2014darwinian}, as well as a hybrid empirical-theoretical protocol in \citealp{maccallum2012evolution}).
Among the empirical approaches, some of the most relevant studies to date consist in a series of papers investigating \emph{quotation} transformations in a large corpus of US blog posts, initially collected and studied by \citet{Leskovec09} and further analyzed by \citet{Simmons11} and \citet{omod-mult}.
%They exhibit several types of regularities and propose diffusion-transformation models of the evolution of quotations, which may nonetheless appear to be relatively simplistic from a cognitive viewpoint. One of the main observations in these works is that even for quotations, a type of public representation that should be among the most stable, it is still possible to witness significant transformations. However, these studies address transformations by focusing on the properties of the source of the quotation (\hbox{e.g.} news outlet {vs.} blog), or the surrounding public space (\hbox{e.g.} quotation frequency in the corpus), rather than the very cognitive-level features which may determine or, at least, influence these transformations.
One of the main observations in these works is that even for quotations, a type of public representation that should be among the most stable, it is still possible to witness significant transformations. They essentially examine the effect of some properties of the quotation source (\hbox{e.g.} news outlet {vs.} blog) or of the surrounding public space (\hbox{e.g.} quotation frequency in the corpus). Some diffusion-transformation models have been proposed, yet the very cognitive features which may determine or, at least, influence these transformations, are overlooked; which may appear to be relatively unsatisfying from a cognitive viewpoint.

At this level, we have to turn to the broader psycholinguistic literature which provides one of the main cognitive foundations for public representation evolution by studying the influence of word features on the ease of recall.
This field is well developed and details the impact that classical psycholinguistic variables such as word frequency~\citep[see][for a review]{Yonelinas02}, age-of-acquisition~\citep{Zevin02}, number of phonemes or number of syllables~\citep[see for instance][]{Rey98,nick-diss}, have in this type of task.

Less classical linguistic variables, based on the study of semantic network properties, have recently started to be used, in the context of connectionism and its normative processual models~\citep[see for instance][]{collins1975spreading}.
Let us mention four interesting studies on that matter, which demonstrate in a strictly \emph{in vitro} framework and at the vocabulary level that properties computed on a word network are important factors for the cognitive processes and reproduction of those words.
First, \citet{Griffiths07} analyze a task where subjects are asked to name the first word which comes to their mind when they are presented with a random letter from the %Latin
alphabet. The authors show that there exists a link between the ease of recall of words and one of their semantic features, namely their authority position (pagerank) in a language-wide semantic network built from external word association data.
\citet{austerweil2012human} further develop this idea by showing that random walk on such a semantic network, that is the exact process measured by the pagerank index, gives a parsimonious account of some semantic retrieval effects (namely, related items being retrieved together).
A third psycholinguistic study by \citet{Chan10} shows, in a picture-naming task, that words are produced faster and with fewer mistakes when they have a lower clustering coefficient in an underlying phonological network (which, again, is  defined from external phonological data).
\citet{nelson2013activation}, finally, show the importance of clustering coefficient in a semantic network by studying the role it plays in a variety of recall and recognition tasks (extralist and intralist cuing, single item recognition, and primed free assocation).

On the whole, the current psycholinguistic state-of-the-art seems to hint towards two antagonistic types of results.
On one hand, part of the literature tends to show that recall is easier for the least ``awkward'' words; those whose age of acquisition is earlier, length is smaller, semantic network position is more central -- this is particularly true in tasks where participants are asked to form spontaneous associations or utter a word in response to a given signal.
On the other hand, when the task consists in recognizing a specific item in a list, ``awkward'' words are actually more easily remembered, possibly as they are more informative and plausibly more discernible~\citep[see again][for a review]{Yonelinas02}.
The jury is still out as to whether reformulation alteration, that is spontaneous replacement of words when asked to repeat a given utterance, is rather of the former or latter sort.
We also aim here at shedding some light on this debate, considering oddness as a dimension of the purported fitness of utterances.

### 2015-03-05 brains-protocol.tex

We used a quotation dataset collected by \citet{Leskovec09}, large enough to lend itself to statistical analysis.
This dataset consists of the daily crawling of news stories and blog posts from around a million online sources, with an approximate publication rate of 900k texts per day, over a nine-month period of time (from August 2008 to April 2009) \cite{Leskovec09-url}.\footnote{Unfortunately, the original article~\citep{Leskovec09} does not provide additional details on the source selection methodology.}
Quotations were then automatically extracted from this corpus: each quotation is a more or less faithful excerpt of an utterance (oral or written) by the quoted person. For instance,
\begin{quote}
The Bank of England said, ``these operations are designed to address funding pressures over quarter-end.''
\end{quote}
Quotations were then gathered in a graph and connected according to their similarity: either because they differ by very few words (in that case, no more than one word) or because they share a certain sequence of words (in that case, at least ten consecutive words). We find for example the following variation of the above quote: \begin{quote}``these operations are \textbf{intended} to address funding pressures over quarter-end.''\end{quote}
A community detection algorithm was applied to that quotation graph to detect aggregates of tightly connected, that is sufficiently similar, groups of quotations (see \citet{Leskovec09} for more detail).
This analysis yielded the final data we had access to, with a total of about \num{70000} sets of quotations; each of these sets allegedly contains all variations of a same parent utterance, along with their respective publication URLs and timestamps.

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around casual expressions, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
To filter them out, we exclude all quotes having less than 5 words long or lasting more than 80 days %\seb{it is asymmetrical...}
 (as well as quotes not written in English). If an entire cluster still lasts more than 80 days after this screening (because of short-lived but unrelated quotes far apart in time), we also exclude it.
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 45,749 clusters (out of 71,568; i.e. 63.9\%), containing a total of 127,778 unique quotes (out of 310,457; i.e. 41.2\%) making up $\sim$2.43m occurrences (out of 8.16m, i.e. 29.8\%).\footnote{The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.}
%We contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion, 
Even if we lose some real event-related utterances which are present in clusters lasting more than 80 days (such as ``the city is tired of me and the organization and I have run our course together''), we check that our approach essentially fulfills its goals by manually coding a random subsample of 100 excluded clusters: a solid 71\% appear to be entirely irrelevant to our analysis (everyday language rather than quotations), and all but one of the remaining clusters were of relevance to the protocol \TB{set out below.}% in Sec.~\ref{sec:model}.

@@

\begin{APAitemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, known to be relevant for both recognition and recall~\citep{gregg1976word},
    \item \textbf{Age of Acquisition}: the average age at which words are learned (obtained from~\citet{Kuperman12}), known to have different effects than word frequency~\citep{morrison1995roles,dewhurst1998separate},
    \item The average \textbf{Number of Phonemes} and \textbf{Number of Syllables} for all pronunciations of a word (obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98})\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.} as a proxy to word production cost,
    \item The average \textbf{Number of Synonyms} for all meanings of a word (obtained from \citet{WordNet10}) as an \emph{a priori} indicator of how easy it would be to replace a word.
\end{APAitemize}

@@

\medskip
%, we thus considered more recently studied variables based on semantic network properties.
We relied on the ``free association'' (FA) norms collected by~\citet{Nelson04} which naturally embed information on the idea association process underlying transformation of quotations. FA norms record the words that come to mind when someone is presented with a given cue% (that is the ``free association'' task)
. As \citet{Nelson04} explain, ``free association response probabilities index the likelihood that one word can cue another word to come to mind with minimal contextual constraints in effect.''
%Following \citet{Griffiths07}, we first consider the directed weighted network formed by the association norms, that is the network where words are nodes and edges are directed from cue to associated word, with a weight equal to the probability of that target word being produced when this particular cue was presented.
% \rk{we're in fact using the unweighed version of the network. Why?}
%Following \citet{Griffiths07}, we first build a directed unweighted network based on association norms, where words are nodes and edges are directed from cue to target word whenever a target word is being produced when this particular cue word was presented.
Following \citet{Griffiths07}, we first build a directed unweighted network based on association norms, where nodes are words and edges are directed from cue to target word whenever the considered target word was produced in response to the considered cue word.
This network is of particular interest since it measures the \emph{in-vitro forced-choice} version of a substitution whereas the data we analyze is the \emph{in-vivo spontaneous} version of what we otherwise hypothesize to be the same process.

@@

\begin{APAitemize}
    \item \textbf{Degree centrality}, measured by the number of cues for which a given word is triggered as a target, and a corresponding generalized measure, node \emph{pagerank}~\citep{Page99}, which has already been used on the FA network by~\citet{Griffiths07}.
    In the present case these two polysemy-related measures are quasi-perfectly correlated. %, and measure polysemy by taking into account the structure of the entire network.
    %However in the present case there is a quasi-perfect correlation between node incoming degree and node \emph{pagerank}~\citep{Page99}, which will lead us to favour the latter later on. Word pagerank on the FA network had already been used by~\citet{Griffiths07}; it may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the pagerank sense are words often selected as targets when presented with cues themselves often selected as targets, and so on recursively.
    \item \textbf{Betweenness centrality}, another measure of node centrality describing the extent to which a node connects otherwise remote areas of the network~\citep{free:set}.
    This quantity tells us if some words behave like unavoidable waypoints on association chains connecting one word to another.
    \item \textbf{Clustering coefficient}, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes~\cite{watt-coll}, computed on the undirected version of the FA network.\footnote{The Clustering coefficient is formally defined as the ratio between the number of actual versus possible edges between a node's neighbors.}
    This tells us if a word belongs more or less to a local aggregate of equivalent words (from a ``free association'' point of view).
\end{APAitemize}

@@

The number of phonemes and the number of syllables naturally exhibit a strong linear correlation ($.8$).
Our analysis showed clearer results with number of phonemes over number of syllables, which is consistent with~\citet{nick-diss}, and we therefore chose to only present results for the former.

>>>>

We used a quotation dataset collected by \citet{Leskovec09}, large enough to lend itself to statistical analysis.
This dataset consists of the daily crawling of news stories and blog posts from around a million online sources, with an approximate publication rate of 900k texts per day, over a nine-month period of time (from August 2008 to April 2009~---~\citealp{Leskovec09-url}).\footnote{Unfortunately, the original article~\citep{Leskovec09} does not provide additional details on the source selection methodology.}
Quotations were then automatically extracted from this corpus: each quotation is a more or less faithful excerpt of an utterance (oral or written) by the quoted person. For instance,
\begin{quote}
The Bank of England said, ``these operations are designed to address funding pressures over quarter-end.''
\end{quote}
Quotations were then gathered in a graph and connected according to their similarity: either because they differ by very few words (in that case, no more than one word) or because they share a certain sequence of words (in that case, at least ten consecutive words). We find for example the following variation of the above quote: \begin{quote}``these operations are \textbf{intended} to address funding pressures over quarter-end.''\end{quote}
A community detection algorithm was applied to that quotation graph to detect aggregates of tightly connected, that is sufficiently similar, groups of quotations~\citep[see][for more detail]{Leskovec09}.
This analysis yielded the final data we had access to, with a total of about \num{70000} sets of quotations; each of these sets allegedly contains all variations of a same parent utterance, along with their respective publication URLs and timestamps.

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around casual expressions, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
To filter them out, we exclude all quotes having less than 5 words long or lasting more than 80 days %\seb{it is asymmetrical...}
 (as well as quotes not written in English). If an entire cluster still lasts more than 80 days after this screening (because of short-lived but unrelated quotes far apart in time), we also exclude it.
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 45,749 clusters (out of 71,568; i.e. 63.9\%), containing a total of 127,778 unique quotes (out of 310,457; i.e. 41.2\%) making up about 2.43m occurrences (out of 8.16m, i.e. 29.8\%).\footnote{The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.}
%We contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion, 
Even if we lose some real event-related utterances which are present in clusters lasting more than 80 days (such as ``the city is tired of me and the organization and I have run our course together''), we check that our approach essentially fulfills its goals by manually coding a random subsample of 100 excluded clusters: a solid 71\% appear to be entirely irrelevant to our analysis (everyday language rather than quotations), and all but one of the remaining clusters were of relevance to the protocol \TB{set out below.}% in Sec.~\ref{sec:model}.

@@

\begin{APAitemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, known to be relevant for both recognition and recall~\citep{gregg1976word},
    \item \textbf{Age of Acquisition}: the average age at which words are learned~\citep[obtained from][]{Kuperman12}, known to have different effects than word frequency~\citep{morrison1995roles,dewhurst1998separate},
    \item The average \textbf{Number of Phonemes} and \textbf{Number of Syllables} for all pronunciations of a word (obtained from the Carnegie Mellon University Pronouncing Dictionary, \citealp{Weide98})\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.} as a proxy to word production cost,
    \item The average \textbf{Number of Synonyms} for all meanings of a word~\citep[obtained from][]{WordNet10} as an \emph{a priori} indicator of how easy it would be to replace a word.
\end{APAitemize}

@@

\medskip
%, we thus considered more recently studied variables based on semantic network properties.
We relied on the ``free association'' (FA) norms collected by \citet{Nelson04} which naturally embed information on the idea association process underlying transformation of quotations. FA norms record the words that come to mind when someone is presented with a given cue% (that is the ``free association'' task)
. As \citet{Nelson04} explain, ``free association response probabilities index the likelihood that one word can cue another word to come to mind with minimal contextual constraints in effect.''
%Following \citet{Griffiths07}, we first consider the directed weighted network formed by the association norms, that is the network where words are nodes and edges are directed from cue to associated word, with a weight equal to the probability of that target word being produced when this particular cue was presented.
% \rk{we're in fact using the unweighed version of the network. Why?}
%Following \citet{Griffiths07}, we first build a directed unweighted network based on association norms, where words are nodes and edges are directed from cue to target word whenever a target word is being produced when this particular cue word was presented.
Following \citet{Griffiths07}, we first build a directed unweighted network based on association norms, where nodes are words and edges are directed from cue to target word whenever the considered target word was produced in response to the considered cue word.
This network is of particular interest since it measures the \emph{in-vitro forced-choice} version of a substitution whereas the data we analyze is the \emph{in-vivo spontaneous} version of what we otherwise hypothesize to be the same process.

@@

\begin{APAitemize}
    \item \textbf{Degree centrality}, measured by the number of cues for which a given word is triggered as a target, and a corresponding generalized measure, node \emph{pagerank}~\citep{Page99}, which has already been used on the FA network by \citet{Griffiths07}.
    In the present case these two polysemy-related measures are quasi-perfectly correlated. %, and measure polysemy by taking into account the structure of the entire network.
    %However in the present case there is a quasi-perfect correlation between node incoming degree and node \emph{pagerank}~\citep{Page99}, which will lead us to favour the latter later on. Word pagerank on the FA network had already been used by~\citet{Griffiths07}; it may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the pagerank sense are words often selected as targets when presented with cues themselves often selected as targets, and so on recursively.
    \item \textbf{Betweenness centrality}, another measure of node centrality describing the extent to which a node connects otherwise remote areas of the network~\citep{free:set}.
    This quantity tells us if some words behave like unavoidable waypoints on association chains connecting one word to another.
    \item \textbf{Clustering coefficient}, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes~\citep{watt-coll}, computed on the undirected version of the FA network.\footnote{The Clustering coefficient is formally defined as the ratio between the number of actual versus possible edges between a node's neighbors.}
    This tells us if a word belongs more or less to a local aggregate of equivalent words (from a ``free association'' point of view).
\end{APAitemize}

@@

The number of phonemes and the number of syllables naturally exhibit a strong linear correlation ($.8$).
Our analysis showed clearer results with number of phonemes over number of syllables, which is consistent with \citet{nick-diss}, and we therefore chose to only present results for the former.
